Flexible Scientific Data Management for Plant Phenomics Research

### 2013-03-11 s4biodiv2013/PODD-S4BIODIV-Submission.tex
apply changed based on David's review

Researchers can describe a data collection, deposit data, choose a license, and
add attribution details. Access to a collection’s description and/or data can be
restricted to CSIRO or a set of individuals (within CSIRO or partner
organisations) or it can be made public, becoming searchable by anyone via the
Internet. In the case where a collection and its data are public, a Digital
Object Identifier (DOI) is issued and can be used to formally cite the
collection in a publication. Collections can either be one-time, self-serve
deposits or automated, ongoing deposits and can be changed over time through
versioning. Whole datasets or specific files within a collection can be
downloaded. A machine-to-machine REST interface permits programmatic search and
collection download.

@@

For PlantScan\textsuperscript{\texttrademark}, file-level metadata
includes plant barcodes, batch numbers, and plant type, although the BagIt
specification does not mandate a particular archiving strategy, with the
focus being upon the directory structure, special files, and integrity checking.
% Bag creation and payload manifest integrity checking, tools can take advantage
% of the multi-core capabilities of modern computing hardware. 
% To suit current
% needs, 
BagIt-conforming tools \cite{Summers} \cite{LoCBagger} were assessed and where necessary,
improvements were implemented and tested to ensure that the tools were scalable with the size of the collections being created. 
% For example, the implementation of \cite{LoCBagger}
% assumed that as many threads as possible should be created for multi-threaded
% operations such as bag creation and payload manifest verification. On a HPC host
% with hundreds of processors, this can lead to runaway thread creation, so this
% needed to be addressed. Neither \cite{Summers} nor \cite{LoCBagger} permitted payload files in a bag to
% be listed. This has since been added to \cite{LoCBagger}. 
%Some functionality (not discussed
%here) present in [8] but not in \cite{Summers} was added to the latter.

@@

CSIRO ASC shared facilities \cite{ASC} are used to process the raw
PlantScan\textsuperscript{\texttrademark} data to derive data products (meshes).
Raw data and meshes are collected using the BagIt format \cite{Kunze2011} and
stored in the ASC archival system. ASC High Performance Compute (HPC) hosts
(systems with high processor count and large memory) are taken advantage of to
create and verify bags more rapidly than would be possible on conventional
computer systems. DAP is used to store collections of
PlantScan\textsuperscript{\texttrademark} 
raw images and processed mesh data as bags. Currently, one bag is equivalent to
a single batch scanned on the
PlantScan\textsuperscript{\texttrademark}
local software system, which usually means the same kind of plant with different
genotypes scanned under one  experiment configuration profile.

>>>>

Researchers can describe a data collection, deposit data, choose a license, and
add attribution details. Access to a collection's description and/or data can be
restricted to CSIRO or a set of individuals (within CSIRO or partner
organisations) or it can be made public, becoming searchable by anyone via the
Internet. In the case where a collection and its data are public, a Digital
Object Identifier (DOI) is issued and can be used to formally cite the
collection in a publication. Collections can either be one-time, self-serve
deposits or automated, ongoing deposits and can be changed over time through
versioning. Whole datasets or specific files within a collection can be
downloaded. A machine-to-machine REST interface permits programmatic search and
collection download.

@@

For PlantScan\textsuperscript{\texttrademark}, file-level metadata
includes plant barcodes, batch numbers, and plant type, although the BagIt
specification does not mandate a particular archiving strategy, with the
focus being upon the directory structure, special files, and integrity checking.
% Bag creation and payload manifest integrity checking, tools can take advantage
% of the multi-core capabilities of modern computing hardware. 
% To suit current
% needs, 
BagIt-conforming tools \cite{Summers} \cite{LoCBagger} were assessed and where necessary,
improvements were implemented and tested to ensure that the tools were fit for purpose in the ASC HPC environment.
% For example, the implementation of \cite{LoCBagger}
% assumed that as many threads as possible should be created for multi-threaded
% operations such as bag creation and payload manifest verification. On a HPC host
% with hundreds of processors, this can lead to runaway thread creation, so this
% needed to be addressed. Neither \cite{Summers} nor \cite{LoCBagger} permitted payload files in a bag to
% be listed. This has since been added to \cite{LoCBagger}. 
%Some functionality (not discussed
%here) present in [8] but not in \cite{Summers} was added to the latter.

@@

CSIRO ASC shared facilities \cite{ASC} are used to process the raw
PlantScan\textsuperscript{\texttrademark} data to derive data products (meshes).
Raw data and meshes are collected using the BagIt format \cite{Kunze2011} and
stored in the ASC archival system. ASC High Performance Compute (HPC) hosts
(systems with high processor count and large memory) are taken advantage of to
create and verify bags more rapidly than would be possible on conventional
computer systems. 
CSIRO's HRPPC makes use of DAP to store collections of PlantScan\textsuperscript{\texttrademark} raw images and processed mesh data as bags.
%DAP is used to store collections of
%PlantScan\textsuperscript{\texttrademark} 
%raw images and processed mesh data as bags. 
Currently, one bag is equivalent to
a single batch scanned on the
PlantScan\textsuperscript{\texttrademark}
local software system, which usually means the same kind of plant with different
genotypes scanned under one  experiment configuration profile.
